Converting LaTeX R Journal Articles into RJ-web-articles

### 2023-06-21 texor.Rmd
Pre-Processing and Post-Processing

### Pandoc Usage

@@

>>>>

### Pandoc does the heavy-lifting

@@

### Pre-Processing : Regular Expressions

LaTeX is very descriptive and allows unfettered levels of customization to authors,
which poses an issue during conversions. RMarkdown is quite a bit restrictive by 
syntax though you can always embed HTML to expand the feature set. Although 
pandoc does most of the heavy lifting, there are some instances where even 
filters cannot assist. A good demonstration of the issue in hand is code 
environments.

A limitation of pandoc is that it only works with a "verbatim" environment. 
However, in "RJournal",  we have multiple custom code environments which are not
supported or defined due to lower-level tex limitations in pandoc. Hence the code 
environments used to be eliminated during the conversion process, including a Lua
filter to find these elements and redefine them as code environments would also 
fail because pandoc would have already tried to process the code inside an unknown 
code environment, leading to missing code elements lost in the conversion.

### Post-Processing : Lua Filters
